\documentclass{article}

\usepackage{booktabs}
\usepackage{float}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{geometry}
\usepackage{syntax}
\usepackage{cite}

\geometry{legalpaper, margin=1in}

\title{SystemVerilog Tools in Python}
\author{Michał Czyż  \\
    PG ETI UE CHIP \\
    \and 
    The Other Dude \\
    His Company / University \\
    }

\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\begin{abstract}
Documentation for SystemVerilog Tools project available at:
\begin{verbatim}
    https:www.github.com/emcezet/sv-tools
\end{verbatim}

\end{abstract}

\section{Introduction}
{ The goal of project is to develop parsing engine for a subsystem of SystemVerilog (SV)
Hardware Description Language (HDL) and provide following utility:
\begin{itemize}
    \item module generation from user-defined templates,
    \item module instantiation from user file,
    \item top level file generation from user files,
    \item simple testbench file generation.
\end{itemize}
Both named port and interface style are accepted. }

\section{Acceptable constructs in SystemVerilog.}

\subsection{Formal syntax.}
{ Formal syntax descriptions use Backus-Naur Form (BNF). This notation was also used in Annex A of \cite{standard}.
Revised and limit list of supported constructs is provided in this section. Please note, that a specific coding
style is expected from users. Curly brackets '\{' and '\}' denote one or more occurence and square '[' ']' denote optional.}

\begin{grammar}
<source_text> ::= [timeunits_declaration] \{description\}
\end{grammar}
\begin{grammar}
<description> ::= <module_declaration>
                  \alt <interface_declaration>
\end{grammar}

\begin{grammar}
<module_declaration> ::= <module_nonansi_header> [ timeunits_declaration ] { module_item }
<endmodule> [ : <module_identifier> ]
\alt <module_ansi_header> [ timeunits_declaration ] { non_port_module_item }
<endmodule> [ : module_identifier ]
\end{grammar}

\begin{grammar}
<module_nonansi_header> ::= { attribute_instance } <module_keyword> [ lifetime ] <module_identifier>
{ package_import_declaration } [ parameter_port_list ] <list_of_ports> ';'
\end{grammar}

\begin{grammar}
<module_ansi_header> ::= { attribute_instance } <module_keyword> [ lifetime ] <module_identifier>
{ package_import_declaration } [ parameter_port_list ] [ list_of_port_declarations ] ;
\end{grammar}

\begin{grammar}
<interface_declaration> ::= <>
\end{grammar}

%\lstinputlisting[language = verilog]{../SVEngine/SVExamples/basic_module.sv}


\section{Usage.}
{ All scripts support -h and --help parameters for usage help.}

\begin{thebibliography}{9}
\bibitem{standard}
8299595,IEEE Std 1800-2017 (Revision of IEEE Std 1800-2012),IEEE Standard for SystemVerilog--Unified Hardware Design, Specification, and Verification Language,
2018,Feb
\bibitem{placeholder}
placeholder

\end{thebibliography}

\end{document}

